\documentclass{resume}

\usepackage[letterpaper,hmargin=0.3in,vmargin=0.2in]{geometry}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Victor Williams}
\address{+234 706 359 7133 \\ Lagos, Nigeria}
\address{\href{mailto:victor.will.chuk@gmail.com}{victor.will.chuk@gmail.com} \\
\href{https://www.victorwilliams.me/}{Portfolio} \\
\href{https://www.linkedin.com/in/victor-williams-chukwudi/}{LinkedIn} \\
\href{https://github.com/victorcodess}{GitHub}}

\begin{document}

\begin{rSection}{Education}

\entrytitle{B.Eng Electrical Engineering}, Covenant University (Second Class Upper) \hfill Nov 2020 — Oct 2025
% Relevant Coursework: Software Development Life Cycle, Introduction to C, Algorithms and Data Structures, Digital Electronics.
\end{rSection}

\begin{rSection}{WORK EXPERIENCE}

\entrytitle{Frontend Engineer} \hfill Apr 2024 — Jan 2026\\
\href{https://contra.com/victorwilliams}{Freelance} (Contra) \hfill \textit{(Remote)}
 \begin{itemize}
    \itemsep -3pt {}
     \item Delivered frontend solutions across 12+ companies—including YC-backed Rulebase, Anyday, and Convoy—spanning website redesigns, CMS migrations, design systems, and interactive dashboards using React, TypeScript, Next.js, and Framer Motion.
 \end{itemize}

\entrytitle{Frontend Engineer} \hfill Mar 2025 — Dec 2025\\
SELECT \hfill \textit{Ontario, Canada (Remote)}
 \begin{itemize}
    \itemsep -3pt {}
     \item Built custom Node.js migration scripts that automated transfer of 100+ content pieces from Markdoc to Sanity CMS, preserving all custom components and reducing manual work by 95\%.
    \item Delivered complete website redesign across 20+ pages using Next.js and TypeScript, implementing modern design system with advanced animations and full responsive optimization.
    \item Designed comprehensive Sanity schema architecture supporting 10+ custom content types with rich text, media management, and dynamic references for flexible content creation
 \end{itemize}

\entrytitle{Frontend Engineering Intern} \hfill Mar 2024 — Aug 2024\\
Korapay \hfill \textit{Lagos, Nigeria}
 \begin{itemize}
    \itemsep -3pt {}
     \item Engineered a responsive 4-page web application using React, TypeScript, and Tailwind CSS, enabling users to explore and reserve over 100 camping spots across Africa.
    \item Designed and integrated a custom backend using NocoDB, manually populating the database with detailed information for over 50 unique camp locations, enhancing booking accuracy by 40\%.
    \item Created a robust search functionality by integrating Google Maps API with auto-complete and country filters, increasing user search precision by 45\%.
 \end{itemize}

\entrytitle{Frontend Engineering Intern} \hfill Aug 2023 — Oct 2023\\
Mono \hfill \textit{Lagos, Nigeria}
 \begin{itemize}
    \itemsep -3pt {}
     \item Implemented the user interface of Mono's Developer Docs sidebar, creating a 100\% responsive design with highly reusable UI components, while optimizing page routing and overall navigation experience.
    \item Developed the frontend of an internal tool for labelling 490,000+ transactions, using Preact and TypeScript. This aided in training the Transaction Metadata Classifier, improving credit scoring models and loan default predictions.
    \item Consumed 16 API endpoints on the backend to efficiently retrieve, create, and update transaction data, adhering to best practices for optimal performance and user experience.
 \end{itemize}

\end{rSection}

\begin{rSection}{PROJECTS}

\entrylink{https://orin.chat/}{Orin} \hfill Jun 2026 \\[0.1cm]
 Voice-enabled AI companion users can text and call in a single thread, with personality customization and persistent history. Built with Next.js, TypeScript, Node.js, Supabase, Zustand, Tanstack Query, Vercel AI SDK, and ElevenLabs
\begin{itemize}
    \itemsep -3pt {}
    \item Built a Node.js voice sidecar linking ElevenLabs Speech Engine to OpenAI streaming via shared prompt/history code, persisting voice turns to Postgres with serialized writes and STT dedup.
   %  \item Developed streaming chat with edit/regenerate, Scribe dictation, read-aloud TTS (Supabase Storage cache), and a WebRTC overlay merging live voice transcripts into one thread.
    \item Implemented quota metering and BYOK (AES-256-GCM), Google OAuth with anonymous session merge, API rate limits, and Vitest tests for quota, crypto, and redirect paths.
\end{itemize}

\entrylink{https://nexus-ui.dev/}{Nexus UI} \hfill Feb 2026 \\[0.1cm]
Open-source React component library for building AI applications; Distributed via the shadcn/ui registry. \textbf{100+ stars} on GitHub
\begin{itemize}
    \itemsep -3pt {}
    \item Implemented composable UI primitives in React and TypeScript on Radix and Tailwind v4—prompt input, model selector, suggestion chips, attachments, Streamdown messages, stick-to-bottom thread, citation previews, and more.
   %  \item Built a RAG-powered AI chat for the Nexus UI docs site, retrieving documentation at request time to deliver grounded, streamed answers with source citations on a public, rate-limited endpoint.
    \item Published an MDX powered documentation site with runnable demos, component API reference, Vercel AI SDK guides, Agent Skills, MCP setup, and llms.txt endpoints for AI tools.
\end{itemize}

\end{rSection}

\begin{rSection}{TECHNICAL SKILLS}

\begin{tabular}{ @{} >{\entrytitlefontsize\bfseries}l @{\hspace{6ex}} p{0.70\textwidth}  }
Web \& Core Technologies & HTML/CSS, JavaScript/TypeScript, React, Next.js, Tailwind CSS, Redux, GraphQL, REST APIs, Node.js, Git/GitHub, Figma, Framer Motion, Sanity CMS, Supabase, Auth.js, Shadcn. \\
\end{tabular}

\end{rSection}

\begin{rSection}{VOLUNTEERING EXPERIENCE}
   \textbf{Lead} \hfill May 2024 — Jul 2025\\
   Google Developer Group, Covenant University \hfill \textit{Ogun, Nigeria}
    \begin{itemize}
       \itemsep -3pt {} 
       \item Led GDG, Covenant University, growing community engagement to 1000+ members through organizing 50+ workshops, study jams, and tech events, including co-organizing TechFest—the university's largest tech conference.
   
    \end{itemize}
    
    \end{rSection}

\end{document}
